---
title: "Purpose of this Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Purpose of this Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MyPackage)
```

# Introduction

This package includes various functions and data that I've saved during my labs for MATH 4753.

#Functions

## myboot

Myboot takes a sample and generates a histogram  including interval estimates and the mean.

```{r}
sam=rnorm(25,mean=25,sd=10)
myboot(sam,iter=10000,alpha=0.05)
```


## mychisim

```{r}
mychisim(n1=10,iter=100,sigma1=4,mean1=10)
```


## mycltu

This function creates a histogram of sample means including a sample and theoretical density curve.

```{r}
mycltu(n=20,iter=10000)
```


## mymaxlik

Mymaxlik gives the maximum likelihood estimate given a set of numbers, a function, and an increment. It also outputs the index of the maximum.

```{r}
y=c(3,3,4,3,4,5,5,4)
logbin=function(x,param) log(dbinom(x,prob=param,size=10))
mymaxlik(lfun=logbin, x=y, param=seq(0,1, length=1000), main="Binomial, n=20")
```


## myncurve

Myncurve displays a graph representing the area under a curve given a mean and standard deviation, up to a specific x value.

```{r}
myncurve(mu=2,sigma=3,a=3)
```


## mysample

Mysample displays iter number of graphs of the distribution of random samples for a given n-value.

```{r}
mysample(n=10,iter=5)
```


## myTsim

```{r}
myTsim(n1=10,iter=100,sigma1=4,mean1=10,ymax = 0.4)
```

